2024 US Presidential Election Forecast Model

### 2024-11-02 paper/paper.qmd

---
title: "2024 US Presidential Election Forecast Model"
subtitle: "My subtitle if needed"
author: 
  - Viet Nguyen
  - Yihang Xu
  - Doran Wang
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
toc-title: "Table of Contents"
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}

@@

clean_data |>
  head(5) |>
  kable(col.names = c("Pollster","Display Name","Pollster Rating ID","Grade","Poll Score", "Transparency Score","State","Start Date","End_Date", "Sample Size", "Election Date", "Party", "Answer","Candidate Name","Percentage"),
    booktabs = TRUE
  )

```

@@

ggplot(clean_data, aes(x = answer)) +
  geom_bar(fill = "red", color = "black") +
  labs(title = "Distribution of Answers", x = "Answer", y = "Count") +
  theme_minimal()
```

```{r}
#| label: fig-histrpct
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

ggplot(clean_data, aes(x = answer, y = pct, fill = party)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Percentage of Support for Each Candidate", x = "Candidate", y = "Percentage") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) + # Converts y-axis to percentage format
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
```

@@

>>>>

---
title: "2024 US Presidential Election Forecast Model"
subtitle: "My subtitle if needed"
author: 
  - Viet Nguyen
  - Yihang Xu
  - Doran Wang
thanks: "Code and data are available at: [https://github.com/vietng04/2024-US-Presidential-Election-Forecast](https://github.com/vietng04/2024-US-Presidential-Election-Forecast)."
date: today
date-format: long 
abstract: "This paper uses aggregate polling data and 'STH' modeling methods to predict the 2024 U.S. presidential election outcome. The Model use the factors related to the polls on Donald Trump’s support rate. The study also includes a deep-dive analysis of methodology on selected pollster, the New York Times (NYT), and then an idealized methodology and survey for predicting elections on a limited budget."
format: pdf
toc: true
toc-title: "Table of Contents"
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}
The data used in this paper came from the FiveThirtyEight [@fivethirtyeight2024]. Data were cleaned and analyzed using the open source statistical programming language R [@citeR]. Libraries `tidyverse` [@citeTidyverse], `janitor` [@Citejan], `knitr` [@citeknitr], and `dplyr` [@citedplyr] were used for simulating, cleaning and testing. Graphics were made using `ggplot2` [@citeGG].

## Sample Data

@@

clean_data |>
  select(1:5) |>      # Select the first 3 columns
  head(5) |>
  kable(
    col.names = names(clean_data)[1:5],  # Automatically get the first 3 column names to match data
    booktabs = TRUE
  )
```

@@

ggplot(clean_data, aes(x = answer)) +
  geom_bar(fill = "red", color = "black") +
  labs(x = "Answer", y = "Count") +
  theme_minimal()
```

```{r}
#| label: fig-histogram_pct
#| fig-cap: Percentage of Support for Each Candidate
#| echo: false
#| warning: false
#| message: false

ggplot(clean_data, aes(x = answer, y = pct, fill = party)) +
  geom_bar(stat = "identity", color = "black") +
  labs( x = "Candidate", y = "Percentage") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) + # Converts y-axis to percentage format
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
```

@@

\appendix
